---
title: "dataSplit"
author: "Josh Erickson"
date: "April 15, 2020"
output: html_document
---

```{r setup, include=FALSE}

library(caret)
library(CAST)
library(sf)
```

## Model Selection  

**Model Splitting**  

```{r, eval = FALSE}


set.seed(1234)
#split data into training and test data. 75% for training and validation. 25% for feature selection. 
dat34index <- createDataPartition(data34$stream, list = FALSE, p=0.75)


train <- data34[dat34index,]

FeatureSelection <- data34[-dat34index,]


```

Another important step in evaluating spatial data is accounting for spatial autocorrelation. We can do this by doing spatial cross validation where folds are created at random; however, when specified (i.e., HUCs, block, cluster) these folds are systematically seperated by k-folds [@roberts2017cross; @valavi2018blockcv]. This will help correct for any spatial autocorrelation in the validation process, which will lead to more realistic results [@meyer2018improving; @meyer2019importance]. The goal is to see how model performances react with different dependance structures. Hence finding a balance between 'too large' and 'too small.' Below we will use the `CAST` package to index these dependance structures. 

```{r, eval=FALSE}
library(CAST)

set.seed(1234)
indicesKsel80 <- CreateSpacetimeFolds(FeatureSelection, spacevar = "spatial_cluster80", k = 10)

set.seed(1234)
indicesKsel40 <- CreateSpacetimeFolds(FeatureSelection, spacevar = "spatial_cluster40", k = 10)


set.seed(1234)
indicesKtrain80 <- CreateSpacetimeFolds(train,spacevar = "spatial_cluster80", k = 10) 

set.seed(1234)
indicesKtrain40 <- CreateSpacetimeFolds(train,spacevar = "spatial_cluster40", k = 10) 

```

Now we can revisit the spread of the hold outs.

```{r, echo=FALSE, fig.align="center"}

data34 <- data34 %>% mutate(id = row_number())

foldId40 <- CreateSpacetimeFolds(data34,spacevar = "spatial_cluster40", k = 10)
foldId80 <- CreateSpacetimeFolds(data34,spacevar = "spatial_cluster80", k = 10)

practice <- melt(foldId40$indexOut)
practice2 <- melt(foldId80$indexOut)
practice <- rename(practice, id = "value", Id40group = "L1")

practice2 <- rename(practice2, id = "value", Id80group = "L1")

practice <- data34 %>% inner_join(practice, by = "id") %>% inner_join(practice2, by = "id")

practice %>% add_count(Id40group, name = "n_40") %>% add_count(Id80group, name = "n_80") %>% add_count(sb_med, name = "n_med") %>% summarise(across(starts_with("n_"), list(mean = mean, median = median, standard_deviation = sd))) %>% t()

```