---
title: "Untitled"
author: "Josh Erickson"
date: "June 24, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(nhdplusTools)
library(exactextractr)
library(tidyverse)
library(conflicted)
```

Bring in some layers "HUC12 to HUC10" to compare and contrast predictions across the landscape. You can also do this with the clusters (80 and 40) as well as the random hold-out. The exploration is endless but the key finding is the accuracy variance of the models and how that is handled/distributed across the landscape.

```{r}

nhdPlushr <- get_nhdplushr(getwd(), "nhdplus.gpkg",
                           layers = c("WBDHU12", "WBDHU10"), overwrite = TRUE, proj = "+proj=aea +lat_1=46 +lat_2=48 +lat_0=44 +lon_0=-109.5 +x_0=600000 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0")

HUC12 <- nhdPlushr$WBDHU12

HUC12 <- st_transform(HUC12, "+proj=aea +lat_1=46 +lat_2=48 +lat_0=44 +lon_0=-109.5 +x_0=600000 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0")

HUC12 <- st_crop(HUC12, c(xmin = 150035.8, xmax = 222365.8, 
                                      ymin = 507390, ymax = 574500 ))
HUC12 <- HUC12 %>% select(Name, AreaSqKM, AreaAcres)

#now extract some zonal statistics from the rasters
HUC12 <- st_cast(HUC12, "POLYGON")


HUC12$mean_def <- exact_extract(deficit, HUC12, 'mean')
ggplot() + geom_sf(data = HUC12,  aes(fill = stdev_def)) + geom_sf(data = DistrictBoundary, fill = NA, col = "black", size = 3)

#now add more
HUC12$mode_def <- exact_extract(deficit, HUC12, 'mode')
HUC12$stdev_def <- exact_extract(deficit, HUC12, function(values, coverage_fraction) sd(values, na.rm = TRUE)) 
HUC12$count_def <- exact_extract(deficit, HUC12, function(values, coverage_fraction)
                            length(values))
#let's add npp since it came up as the 2nd variable in all the models
HUC12$mode_npp <- exact_extract(nppMid30, HUC12, 'mode')
HUC12$mean_npp <- exact_extract(nppMid30, HUC12, 'mean')
HUC12$stdev_npp <- exact_extract(nppMid30, HUC12, function(values, coverage_fraction) sd(values, na.rm = TRUE)) 
HUC12$count_npp <- exact_extract(nppMid30, HUC12, function(values, coverage_fraction)
                            length(values))


```

Now let's bring these zonal stats into the resamples to explore some trends with deficit and stream expression. This is just a 'hack' way of exploring accuracy within different zones/aggregations.

```{r}


join_all80 <- st_as_sf(join_all80, coords = c("utm1", "utm2"))

join_all80 <- join_all80 %>% st_set_crs(proj.study) 

join_all80 <- st_transform(join_all80, "+proj=aea +lat_1=46 +lat_2=48 +lat_0=44 +lon_0=-109.5 +x_0=600000 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0")


join_80intersect <- st_intersection(join_all80, HUC12)


join_all40 <- st_as_sf(join_all40, coords = c("utm1", "utm2"))

join_all40 <- join_all40 %>% st_set_crs(proj.study) 

join_all40 <- st_transform(join_all40, "+proj=aea +lat_1=46 +lat_2=48 +lat_0=44 +lon_0=-109.5 +x_0=600000 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0")

join_40intersect <- st_intersection(join_all40, HUC12)


join_allnoSD <- st_as_sf(join_allnoSD, coords = c("utm1", "utm2"))

join_allnoSD <- join_allnoSD %>% st_set_crs(proj.study) 

join_allnoSD <- st_transform(join_allnoSD, "+proj=aea +lat_1=46 +lat_2=48 +lat_0=44 +lon_0=-109.5 +x_0=600000 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0")

join_noSDintersect <- st_intersection(join_allnoSD, HUC12)

```


```{r}
summary_80 <- join_80intersect %>% group_by(mode_def) %>%
                     mutate(pred_if = ifelse(pred_topoclimatic ==                                       obs_topoclimatic, 1, 0),
                            Topoclimatic_rate = sum(pred_if)/n(),
                            pred_if_topo = ifelse(pred_topo_only ==                                     obs_topo_only, 1, 0),
                            Topo_rate = sum(pred_if_topo)/n(),
                            NHDPlus_if = ifelse(NHDPlus == obs_topoclimatic,                                                            1, 0),
                            NHDPlus_rate = sum(NHDPlus_if)/n()) %>% 
  
              summarise(Topo_rate = mean(Topo_rate),
                        NHDPlus_rate = mean(NHDPlus_rate),
                        Topoclimatic_rate = mean(Topoclimatic_rate),
                        count = n())

summary_80_clust <- join_80intersect %>% group_by(spatial_cluster80) %>%
                     mutate(pred_if = ifelse(pred_topoclimatic == obs_topoclimatic, 1, 0),
                            Topoclimatic_rate = sum(pred_if)/n(),
                            pred_if_topo = ifelse(pred_topo_only == obs_topo_only, 1, 0),
                            Topo_rate = sum(pred_if_topo)/n(),
                            NHDPlus_if = ifelse(NHDPlus == obs_topoclimatic, 1, 0),
                            NHDPlus_rate = sum(NHDPlus_if)/n()) %>% 
              summarise(Topo_rate = mean(Topo_rate),
                        NHDPlus_rate = mean(NHDPlus_rate),
                        Topoclimatic_rate = mean(Topoclimatic_rate),
                        count = n(),
                        meanDef = mean(deficitRS),
                        meanNPP = mean(nppmmid30agg))

summary_40 <- join_40intersect %>% group_by(mode_def) %>%
                     mutate(pred_if = ifelse(pred_topoclimatic == obs_topoclimatic, 1, 0),
                            Topoclimatic_rate = sum(pred_if)/n(),
                            pred_if_topo = ifelse(pred_topo_only == obs_topo_only, 1, 0),
                            Topo_rate = sum(pred_if_topo)/n(),
                            NHDPlus_if = ifelse(NHDPlus == obs_topoclimatic, 1, 0),
                            NHDPlus_rate = sum(NHDPlus_if)/n()) %>% 
              summarise(Topo_rate = mean(Topo_rate),
                        NHDPlus_rate = mean(NHDPlus_rate),
                        Topoclimatic_rate = mean(Topoclimatic_rate),
                        count = n())

summary_40_clust <- join_80intersect %>% group_by(spatial_cluster40) %>%
                     mutate(pred_if = ifelse(pred_topoclimatic == obs_topoclimatic, 1, 0),
                            Topoclimatic_rate = sum(pred_if)/n(),
                            pred_if_topo = ifelse(pred_topo_only == obs_topo_only, 1, 0),
                            Topo_rate = sum(pred_if_topo)/n(),
                            NHDPlus_if = ifelse(NHDPlus == obs_topoclimatic, 1, 0),
                            NHDPlus_rate = sum(NHDPlus_if)/n()) %>% 
              summarise(Topo_rate = mean(Topo_rate),
                        NHDPlus_rate = mean(NHDPlus_rate),
                        Topoclimatic_rate = mean(Topoclimatic_rate),
                        count = n(),
                        meanDef = mean(deficitRS),
                        meanNPP = mean(nppmmid30agg))


summary_noSD <- join_noSDintersect %>% group_by(mode_def) %>%
                     mutate(pred_if = ifelse(pred_topoclimatic == obs_topoclimatic, 1, 0),
                            Topoclimatic_rate = sum(pred_if)/n(),
                            pred_if_topo = ifelse(pred_topo_only == obs_topo_only, 1, 0),
                            Topo_rate = sum(pred_if_topo)/n(),
                            NHDPlus_if = ifelse(NHDPlus == obs_topoclimatic, 1, 0),
                            NHDPlus_rate = sum(NHDPlus_if)/n()) %>% 
              summarise(Topo_rate = mean(Topo_rate),
                        NHDPlus_rate = mean(NHDPlus_rate),
                        Topoclimatic_rate = mean(Topoclimatic_rate),
                        count = n(),
                        defMean = mean(deficitRS))

summary_noSD_clust <- join_noSDintersect %>% group_by() %>%
                     mutate(pred_if = ifelse(pred_topoclimatic == obs_topoclimatic, 1, 0),
                            Topoclimatic_rate = sum(pred_if)/n(),
                            pred_if_topo = ifelse(pred_topo_only == obs_topo_only, 1, 0),
                            Topo_rate = sum(pred_if_topo)/n(),
                            NHDPlus_if = ifelse(NHDPlus == obs_topoclimatic, 1, 0),
                            NHDPlus_rate = sum(NHDPlus_if)/n()) %>% 
              summarise(Topo_rate = mean(Topo_rate),
                        NHDPlus_rate = mean(NHDPlus_rate),
                        Topoclimatic_rate = mean(Topoclimatic_rate),
                        count = n(),
                        defMean = mean(deficitRS))

summary_80_clust  %>% pivot_longer(cols = ends_with("rate"), "Model", "value") %>% ggplot(aes(meanDef, value, color = Model)) + geom_point() + geom_smooth(method = "lm") + facet_wrap(~Model)

summary_40_clust  %>% pivot_longer(cols = ends_with("rate"), "Model", "value") %>% ggplot(aes(meanNPP, value, color = meanDef)) + geom_point() + geom_smooth(method = "lm") + facet_wrap(~Model)

summary_noSD  %>% pivot_longer(cols = ends_with("rate"), "Model", "value") %>% ggplot(aes(defMean, value, color = Model)) + geom_point() + geom_smooth(method = "lm") + facet_wrap(~Model)

```

```{r}
join_40intersect %>% ggplot() + geom_hex(aes(deficitRS,nppmmid30agg))
```

