---
title: "FFS RF"
author: "Josh Erickson"
date: "April 14, 2020"
output: html_document
---

```{r setup, include=FALSE}

load("D:/Rcodes/Water_Prediction/Hird_Water_Prediction/waterD/waterPred/workingThoughProject/workingthroughproj.RData")
library(sp)
library(rgdal)
library(rgeos)
library(raster)
library(automap)
library(caret)
library(CAST)
library(blockCV)
library(tidyverse)
library(gridExtra)
library(reshape2)
library(doParallel)
library(parallel)
library(mlbench)
library(plotROC)
library(pdp)
library(vip)
library(gridGraphics)
library(grid)
```

#### FFS Random Forest

So with the FFS we will just use the default parameters for both Random Forest and GBM. This shouldn't be too big of concern as I mentioned earlier. Kappa will still be the performance metric for selecting. First we need to prep the PCA variables before we do ffs. 

```{r, eval=FALSE}


predictorsRF <- trainsel[,c("twi30agg","tpi30agg","accum30","vv30agg", "vvsd30agg","npol30agg","ndvi30yrRS", "ndvias30agg", "ndwias30agg","nppmmid30agg","deficitRS","cad30RS","decid30RS","cpg30precip", "B2_30agg","B4_30agg","B8_30agg")]

responseRF <- trainsel$stream

```

*FFS 12th HUC Random Forest*

```{r eval=FALSE}
#bring in cores
cluster <- makeCluster(detectCores() - 1) # convention to leave 1 core for OS
registerDoParallel(cluster)

#set up control
ctrl12rf <- trainControl(method="repeatedcv",
                     repeats = 5,number = 10,
                     allowParallel = TRUE,
                     returnResamp = "all", 
                     verbose = FALSE, 
                     index = indices12sel$index)

set.seed(1234)
ffs12rf.hw <- ffs(predictorsRF,responseRF, 
  metric = "Kappa",
  method = "rf",
  minVar = 3, 
  trControl = ctrl12rf)

#now remove cluster. consistency...
stopCluster(cluster)
registerDoSEQ()

```

```{r echo=FALSE, eval=TRUE, message=FALSE, fig.align='center', fig.height=6, fig.width=16}
#now plot
plot_ffsCust(ffs12rf.hw, size =4, pch = 19,lwd = .1) + ggtitle("FFS 12th HUC Random Forest Balanced")
```

```{r echo=FALSE, eval=TRUE, message=FALSE, fig.align='center', fig.height=6, fig.width=10}

plot_ffsCust(ffs12rf.hw,plotType = "selected", main = "FFS 12th HUC Random Forest Balanced",cex.axis=1.5, cex.lab=1.5)
```



*FFS BlockCV Medium Random Forest*

```{r eval=FALSE}
#bring in cores
cluster <- makeCluster(detectCores() - 1) # convention to leave 1 core for OS
registerDoParallel(cluster)

#set up control
ctrlMedrf <- trainControl(method="repeatedcv",
                     repeats = 5,number = 10,
                     allowParallel = TRUE,
                     returnResamp = "all", 
                     verbose = FALSE, 
                     index = indicesMedsel$index)

#run
set.seed(1234)
ffsMedrf.hw <- ffs(predictorsRF,responseRF, 
  metric = "Kappa",
  method = "rf",
  trControl = ctrlMedrf)

#now remove cluster. consistency...
stopCluster(cluster)
registerDoSEQ()

```

```{r echo=FALSE, eval=TRUE, message=FALSE, fig.align='center', fig.height=8, fig.width=16}
#now plot
plot_ffsCust(ffsMedrf.hw, size =4, pch = 19,lwd = .1) + ggtitle("FFS BlockCV Medium Random Forest Balanced")

```

```{r echo=FALSE, eval=TRUE, message=FALSE, fig.align='center', fig.height=6, fig.width=20}

plot_ffsCust(ffsMedrf.hw,plotType = "selected", main = "FFS BlockCV Medium Random Forest Balanced",cex.axis=1.5, cex.lab=1.5)
```

*FFS 14th HUC Random Forest*

```{r eval=FALSE}
#bring in cores
cluster <- makeCluster(detectCores() - 1) # convention to leave 1 core for OS
registerDoParallel(cluster)

#set up control
ctrl14rf <- trainControl(method="repeatedcv",
                     repeats = 5,number = 10,
                     allowParallel = TRUE,
                     returnResamp = "all", 
                     verbose = FALSE, 
                     index = indices14sel$index)

#run
set.seed(1234)
ffs14rf.hw <- ffs(predictorsRF,responseRF, 
  metric = "Kappa",
  method = "rf",
  trControl = ctrl14rf)

blah
#now remove cluster. consistency...
stopCluster(cluster)
registerDoSEQ()

```
```{r echo=FALSE, eval=TRUE, message=FALSE, fig.align='center', fig.height=8, fig.width=16}
#now plot
plot_ffsCust(ffs14rf.hw, size =4, pch = 19,lwd = .1) + ggtitle("FFS 14th HUC Random Forest Balanced")

```

```{r echo=FALSE, eval=TRUE, message=FALSE, fig.align='center', fig.height=6, fig.width=24}

plot_ffsCust(ffs14rf.hw,plotType = "selected", main = "FFS 14th HUC Random Forest Balanced",cex.axis=1.5, cex.lab=1.5)
```

*FFS Kmeans Random Forest*

```{r eval=FALSE}
#bring in cores
cluster <- makeCluster(detectCores() - 1) # convention to leave 1 core for OS
registerDoParallel(cluster)

#set up control
ctrlKrf <- trainControl(method="repeatedcv",
                     repeats = 5,number = 10,
                     allowParallel = TRUE,
                     returnResamp = "all", 
                     verbose = FALSE, 
                     index = indicesKsel$index)
#set up control for prevalence
ctrlKprev <- trainControl(method="repeatedcv",
                     repeats = 5,
                     allowParallel = TRUE,
                     returnResamp = "all", 
                     verbose = FALSE, 
                     index = indicesKselprev$index)
#run
set.seed(1234)
ffsKrf.hw <- ffs(predictorsRF,responseRF, 
  metric = "Kappa",
  method = "rf",
  trControl = ctrlKrf)


#now remove cluster. consistency...
stopCluster(cluster)
registerDoSEQ()
```
```{r echo=FALSE, eval=TRUE, message=FALSE, fig.align='center', fig.height=8, fig.width=16}
#now plot
plot_ffsCust(ffsKrf.hw, size =4, pch = 19,lwd = .1) + ggtitle("FFS Kmeans Random Forest Balanced")
```

```{r echo=FALSE, eval=TRUE, message=FALSE, fig.align='center', fig.height=6, fig.width=20}

plot_ffsCust(ffsKrf,plotType = "selected", main = "FFS Kmeans Random Forest Balanced",cex.axis=1.5, cex.lab=1.5)
```

