---
title: "csvs"
author: "Josh Erickson"
date: "June 26, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Create some csv's from all the data we've generated. First the prediction results from each model.

```{r}

write_csv(resamples.tune80, "resamples.tune80.csv")

write_csv(resamples.tune40, "resamples.tune40.csv")

write_csv(resamples.tunenoSD, "resamples.tunenoSD.csv")

write_csv(resamples.tune80_topo, "resamples.tune80_topo.csv")

write_csv(resamples.tune40_topo, "resamples.tune40_topo.csv")

write_csv(resamples.tunenoSD_topo, "resamples.tunenoSD_topo.csv")
```


These data take the resamples per model, metric, and dependance structure.

```{r}
plotting_40 <- plotting_40 %>% mutate(dependance = "Cluster of 40")

plotting_80 <- plotting_80 %>% mutate(dependance = "Cluster of 80")

noSD_plotting <- noSD_plotting %>% mutate(dependance = "Random Folds")

ci.resamp40per <- ci.resamp40per %>% mutate(dependance = "Cluster of 40")

ci.resamp80per <- ci.resamp80per %>% mutate(dependance = "Cluster of 80")

ci.resampnoSDper <- ci.resampnoSDper %>% mutate(dependance = "Random Folds")

all_resamps <- rbind(ci.resamp40per, ci.resamp80per, ci.resampnoSDper)

write_csv(all_resamps, "all_resamps.csv")

all_plotting <- rbind(plotting_40, plotting_80, noSD_plotting)

write_csv(all_plotting, "all_plotting.csv")

```


This goes a step further and basically joins `all_plotting` and `all_resamps` by combining cofidence intervals with sample mean (resample mean) per model, metric and dependance structure. Good for visualizing.

```{r}

all_resamps <- all_resamps %>% arrange(metric, model) %>%  rowid_to_column("id")

all_plotting <- all_plotting %>% filter(metric %in% c("ROC", "J", "Accuracy", "Kappa", "Sensitivity", "Specificity")) %>% group_by(model,metric, dependance) %>% slice(1) %>% select(-Resample, -value) %>% arrange(metric, model) %>% rowid_to_column("id") 

table_results <- left_join(all_resamps, all_plotting,  by = "id")  %>% rename(Dependance = "dependance.x", Lower = "2.5%", Upper = "97.5%", Sample_Mean = "point_estimate", Metric = "metric.x", Model = "model.x") %>% select(Model, Metric, Lower, Upper, Sample_Mean, Dependance) %>% mutate(across(where(is.numeric), ~round(., digits = 3)))

table_results <- table_results %>% mutate(for_table = paste0(Sample_Mean," ","(",Lower,", ",Upper,")"))


table_results %>% filter(Dependance == "Random Folds") 

write_csv(table_results, "Table_Results.csv")
```


Now if you want all the data at your fingertips (i.e. all predictions, resamples, etc) then use this csv below.

```{r}
join_all40 <- join_all40 %>% mutate(dependance = "Cluster of 40")

join_all80 <- join_all80 %>% mutate(dependance = "Cluster of 80")

join_allnoSD <- join_allnoSD %>% mutate(dependance = "Random Folds")

join_all_raw <- rbind(join_all40, join_all80, join_allnoSD)

write_csv(join_all_raw, "join_all_raw.csv")

```
