---
title: "nhdplus_add_in"
author: "Josh Erickson"
date: "June 10, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(caret)
library(reshape2)
library(stringr)
library(tidyverse)
```

Adding in the NHDPlus data with the resampled locations in the tuning process so we can compare metrics by resample. This is a lot of tedius work but ultimately getting the 'models' all together by CV method.


```{r}

train <- read_csv("data/data34.csv") %>% mutate(across(where(is.character), factor))
#now get points from train data and extract
trainPTS <- st_as_sf(train, coords = c("utm1","utm2"))

st_crs(trainPTS) <- "+proj=aea +lat_1=46 +lat_2=48 +lat_0=44 +lon_0=-109.5 +x_0=600000 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0"

#now give the 0's"X0" and the values "X1"
train$NHDPlus_char <- ifelse(train$NHDPlus == 0, paste("X1"), paste("X2"))

train$NHDPlus_fact <- factor(train$NHDPlus_char)

#now we have baseline data associated with the points used in the models

#now get the best tune to filter for the GBM 10 cluster model topoclimatic 
GBM_k10_4$bestTune

```

```{r}

#now collect resample locations from each tuning process
resamples.GBM_k10_4 <- GBM_k10_4$pred %>% filter(n.trees == 500, interaction.depth == 2, shrinkage == 0.05, n.minobsinnode == 25)  

#add common identifier to training set
train$rowIndex <- seq(1,8802,1)

#now join for train and resamps
join_resamp <- left_join(resamples.GBM_k10_4,train,  by = "rowIndex" )

```

Now we can select the resampled prediction, observations, NHDPlus_fact and resample id.

```{r}
nhdtune <- join_resamp %>% select(obs, NHDPlus_fact, Resample)

```

Now this allows us to run summary statistics on each of the model types, including the NHDPlus response.

```{r}
#create a function to capture the NHDPlus summary stats
#now we can run the stats on it.
twoClassSummaryNHD <- function (data, lev = NULL, model = NULL) 
{
    rocObject <- pROC::roc(as.numeric(data$obs), as.numeric(data$NHDPlus_fact))
    
    rocAUC <- rocObject$auc
    
    out <- c(rocAUC, sensitivity(data[, "NHDPlus_fact"], data[, "obs"], 
        lev[1]), specificity(data[, "NHDPlus_fact"], data[, "obs"], lev[2]))
    names(out) <- c("ROC", "Sens", "Spec")
    out
}
fourStatsNhdtune <-  function(dat) {
  out <- c(twoClassSummaryNHD(dat, lev = levels(dat$obs), model = NULL))
  tab <- caret::confusionMatrix(dat$NHDPlus_fact, dat$obs,
                                positive = levels(dat$obs)[1])
  res <- c(tab$byClass, tab$overall[c("Accuracy", "Kappa")])
  res <- c(res,
           res["Sensitivity"] + res["Specificity"] - 1,
           sqrt((res["Sensitivity"] - 1) ^ 2 + (res["Specificity"] - 1) ^ 2))
  names(res)[-seq_len(length(res) - 2)] <- c("J", "Dist")
  list(out,res)
  
}
```

Now we can run the summary stats on each Resample (group). Start with the 80 cluster.

```{r}


blah <- nhdtune %>% split(.$Resample) %>% map(fourStatsNhdtune)

blah_names <- data.frame(Resample = names(blah))

blah <- blah %>% map_df(unlist)

nhd <- cbind(blah_names, blah)

nhd <- nhd %>% mutate(model = 'NHDPlus')

```





